---
title: "DonorsChoose SQL"
author: "JSG"
date: "2/8/2021"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
pacman::p_load("tidyverse", "magrittr", "nycflights13", "gapminder",
"Lahman", "maps", "lubridate", "pryr", "hms", "hexbin",
"feather", "htmlwidgets", "broom", "pander", "modelr",
"XML", "httr", "jsonlite", "lubridate", "microbenchmark",
"splines", "ISLR", "MASS", "testthat", "caret", "gbm",
"RSQLite", "class", "babynames", "nasaweather", "pls",
"fueleconomy", "viridis", "boot", "devtools", "tree",
"glmnet", "gam", "akima", "factoextra", "randomForest",
"ggrepel", "GGally", "fmsb", "sjPlot", "rcompanion",
"leaps", "caretEnsemble", "dplyr")
```


SQL DATABASE 

```{r}
donation <- readRDS("donation.rds")
```


```{r}
Donors <- read_csv("Donors.csv.zip")
```


```{r}
project <- readRDS("project.rds")
```


```{r}
Resources <- read_csv("Resources.csv.zip")
```

Resources have 8688 parsing failures of 7170289 rows with 5 variables


To see the parsing failures
```{r}
problem <- problems(Resources)
```

```{r}
problem
```
# A tibble: 8,688 x 5
     row col                expected           actual file               
   <int> <chr>              <chr>              <chr>  <chr>              
 1  1171 Resource Item Name delimiter or quote d      'Resources.csv.zip'
 2  3431 Resource Item Name delimiter or quote s      'Resources.csv.zip'
 3  5197 Resource Item Name delimiter or quote l      'Resources.csv.zip'
 4  5226 Resource Item Name delimiter or quote j      'Resources.csv.zip'
 5  6487 Resource Item Name delimiter or quote k      'Resources.csv.zip'
 6  6487 Resource Item Name delimiter or quote k      'Resources.csv.zip'
 7  6487 Resource Item Name delimiter or quote g      'Resources.csv.zip'
 8  7524 Resource Item Name delimiter or quote t      'Resources.csv.zip'
 9  8873 Resource Item Name delimiter or quote k      'Resources.csv.zip'
10  8873 Resource Item Name delimiter or quote f      'Resources.csv.zip'
# ... with 8,678 more rows

To remove the parsing failures (Bjarnes method)
First I define the parsing failures in a dataset called resourses, and I subtract it at the same time
```{r}
resources <- -problems(Resources)[1]%>%
  dplyr::distinct()%>%
  pull()
```

```{r}
resources
```


Then I define a new dataset not containing the parsing failures
```{r}
resource <- Resources[resources,]
```

```{r}
resource
```



```{r}
Schools <- read_csv("Schools.csv.zip")
```
Parsing failure


```{r}
Teachers <- read_csv("Teachers.csv.zip")
```



TAGER SMÅ STIKPRØVER AF DATASÆTTENE

```{r}
set.seed(123)
Donors_1 <- Donors %>% sample_frac(.001)
```

```{r}
Donors_1
```


FLYTTER 6 DATASÆT OVER I EN SQL DATABASE OG KALDER DEN "DONORDATA"


SQL
```{r}

library(RSQLite)
library(testthat)

if (!dir.exists("donordata")) dir.create("donordata")


connection_donordata <- dbConnect(SQLite(), "donordata/r_db_ex.sqlite")

dbWriteTable(connection_donordata, "db_donation", donation, row.names = FALSE, overwrite = TRUE)

dbWriteTable(connection_donordata, "db_Donors", Donors_1, row.names = FALSE, overwrite = TRUE)

dbWriteTable(connection_donordata, "db_project", project, row.names = FALSE, overwrite = TRUE)

dbWriteTable(connection_donordata, "db_resource", resource,  row.names = FALSE, overwrite = TRUE)

dbWriteTable(connection_donordata, "db_Schools", Schools, row.names = FALSE, overwrite = TRUE)

dbWriteTable(connection_donordata, "db_Teachers", Teachers, row.names = FALSE, overwrite = TRUE)



dbListTables(connection_donordata)

dbDisconnect(connection_donordata)


```
[1] "db_Donors"   "db_Schools"  "db_Teachers" "db_donation" "db_project"  "db_resource"

EKSEMPEL MED DONORS DATASÆTTET - SAMME PROCEDURE FOR ALLE DATASÆT

CHECKER OM FILEN DONORS ER I DONORDATA DATABASEN
```{r}
connection_donordata <- dbConnect(SQLite(), "donordata/r_db_ex.sqlite")
dbExistsTable(connection_donordata, "db_Donors")
dbDisconnect(connection_donordata)

```
[1] TRUE

CHECKER VARIABLER
```{r}
connection_donordata <- dbConnect(SQLite(), "donordata/r_db_ex.sqlite")
dbListFields(connection_donordata, "db_Donors")
dbDisconnect(connection_donordata)
```
[1] "Donor ID"         "Donor City"       "Donor State"      "Donor Is Teacher" "Donor Zip" 

KOPIERER DATAFILER TIL Rstudio DATABASEN

```{r}
connection_donordata <- dbConnect(SQLite(), "donordata/r_db_ex.sqlite")
donors_in_our_db <- dbReadTable(connection_donordata, "db_Donors")
dbDisconnect(connection_donordata)

```



